An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-28 draft.tex
Experiment 2

\item Can having a multi-population enabled platform, with heterogeneous populations and
the support for mixing search strategies,  increase the performance of the
search by needing fewer function evaluations than a homogeneous setting?

@@

>>>>

\item Having a multi-population enabled platform, with heterogeneous populations and
the support for mixing search strategies,  increases the performance of the
search by needing fewer function evaluations than a homogeneous setting?

@@

\subsection{Experiment 2}
\label{sec:exp2}
% Experiment 1

Having a multi-population based algorithm can decrease the execution time
because of the parallel execution of the evolution. But, having heterogeneous
populations increases the performance of the search by needing fewer function
evaluations than a homogeneous setting.?

In this experiment, we compare the performance of both heterogeneous and
homogeneous settings. We compare a multi-population with only  GA and PSO
populations, versus an ensemble of GA and PSO algorithms on the first five
functions of the BOBB testbed.  We used ten populations and 8 workers for the
experiment and the same parameters as before.
